Make any stupid plot you want

### 2021-01-18 draft/sections/math.tex
roadmap

%% convention is base space \times fiber bundle
%% change B to K
\section{Notation \& Definitions}

@@

We use fiber bundles\cite{FiberBundle2020, rowlandFiberBundle} to model data and graphics because they allow us to seperate the variables in a dataset from how the values in those fields are connected to each other. The fiber bundles mentioned in this work are assumed to be locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}.

%% we will define data, visual, and graphic spaces in terms of fiberbundles and then describe equivariant maps from E to V to H

\subsection{Data Space}
% introduce what this is gonna happen in this section - we will talk about, fiber and connectivity 
% motivate w/ data/ example - have weather station. %tidydata 
% we will introduce the fiber bundle and its components base and total space to explain the fiber

@@

\subsubsection{Variable Field in F }
\label{sec:fiber_data}
 %%%first sentence should be a paragraph
%%% butler's paper, no notion of distance on K, can only map F to the visual fibers, so need an X to map to Xpos
% variable, measurement, pull in tidy here, 
% % motivate by example, temperature \ time 
%% F_0 = {temp_0, temp_n}, 
%% then adding in a second set of variables time: 
%% F_1 = {time_0, time_1}
% break out into F first as set of values, then F=F_{0}\times F_{1} as component

@@

\subsection{Prerender Space $H$}
\label{sec:display}
We define a graphic space $H$ such that we do not have to assume the physical output space of the renderer. This means that the graphic in $H$ can be output to a screen or 3D printed space or a dome. We model the prerender space as a fiber bundle (H, S, $\pi$, D). $H$ is the predisplay space, with a fiber $D$ dependent on the target display and a base space of $S$.

@@

\subsubsection{Visual Channels}
$\nu: E \rightarrow V$ is an equivariant map such that there is a homomorphism from left monoid actions on $E_{i}$ to left monoid actions on $V_{i}$ where $i$ identifies a field in the fiber. $E_i$ and $V_{i}$ each contain a set of values as defined in $F$ and $P$ respectively. A validly constructed $\nu$ is one where the  diagram 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "m_e"'] & V_i \arrow[d, "m_v"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
commutes such that $\nu_i(m_e(E_i)) = m_v(\nu_i(E_i))$.

@@

\subsubsection{Assembling Marks}
\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}  
\end{figure}

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
As formulated above, every artist function $A$ has fixed $\nu$ and generates a distinct graphic $\rho$. It is unfeasible to implement $A$ for every single graphic; instead we implement the equivalence class of artists $\{A \in A^\prime: A_{1} \equiv A_{2}\}$ which is $Q:\Gamma(V) \rightarrow \Gamma(H)$.

\end{document}

>>>>

\section{Notation \& Definitions}

@@

We use fiber bundles\cite{FiberBundle2020, rowlandFiberBundle} to model data and graphics because they allow us to seperate the variables in a dataset from how the values  are connected to each other. The fiber bundles mentioned in this work are assumed to be locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}.

In this section, we first describe the fiber bundle spaces of data(\ref{sec:data}), graphics(\ref{sec:graphic}), and intermediate visual characteristics (\ref{sec:artist}). We then discuss the equivariant maps between data and visual characteristics (~\ref{sec:artist_nu}) and visual characteristics and graphics (~\ref{sec:artist_q}) that make up the artist.

\subsection{Data Space}
\label{sec:space_data}
% introduce what this is gonna happen in this section - we will talk about, fiber and connectivity 
% motivate w/ data/ example - have weather station. %tidydata 
% we will introduce the fiber bundle and its components base and total space to explain the fiber

@@

\subsubsection{Variable Field in F }
\label{sec:data}
 %%%first sentence should be a paragraph
%%% butler's paper, no notion of distance on K, can only map F to the visual fibers, so need an X to map to Xpos
% variable, measurement, pull in tidy here, 
% % motivate by example, temperature \ time 
%% F_0 = {temp_0, temp_n}, 
%% then adding in a second set of variables time: 
%% F_1 = {time_0, time_1}
% break out into F first as set of values, then F=F_{0}\times F_{1} as component

@@

\subsection{Prerender Space $H$}
\label{sec:graphic}
We define a graphic space $H$ such that we do not have to assume the physical output space of the renderer. This means that the graphic in $H$ can be output to a screen or 3D printed space or a dome. We model the prerender space as a fiber bundle (H, S, $\pi$, D). $H$ is the predisplay space, with a fiber $D$ dependent on the target display and a base space of $S$.

@@

\subsubsection{Visual Channels}
\label{sec:artist_nu}
$\nu: E \rightarrow V$ is an equivariant map such that there is a homomorphism from left monoid actions on $E_{i}$ to left monoid actions on $V_{i}$ where $i$ identifies a field in the fiber. $E_i$ and $V_{i}$ each contain a set of values as defined in $F$ and $P$ respectively. A validly constructed $\nu$ is one where the  diagram 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "m_e"'] & V_i \arrow[d, "m_v"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
commutes such that $\nu_i(m_e(E_i)) = m_v(\nu_i(E_i))$.

@@

\subsubsection{Assembling Marks}
\label{sec:artist_q}
\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}  
\end{figure}

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
As formulated above, every artist function $A$ has fixed $\nu$ and generates a distinct graphic $\rho$. It is unfeasible to implement $A$ for every single graphic; instead we implement the equivalence class of artists $\{A \in A^\prime: A_{1} \equiv A_{2}\}$ which is $Q:\Gamma(V) \rightarrow \Gamma(H)$. 
\end{document}
